### 2019-10-22 Manuscript/pole_table.tex
add f factor calculations and strat adding updated Chuar poles

             Laurentia-Wyoming &                       Sourdough mafic dike swarm &      A &    -108.3 &      44.7 & 292.0 &  49.2 &       8.1 &     1899\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Kilian2016a\} \\

@@

                     Laurentia &                                    Dubawnt Group &      B &     265.6 &      64.1 & 277.0 &   7.0 &       8.0 &   1785\$\textasciicircum \{+35\}\$\$\_\{-35\}\$ &                                    \textbackslash cite\{Park1973\} \\

@@

                     Laurentia &                                    Cleaver Dykes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Irving2004\} \\

@@

                     Laurentia &                          Western Channel Diabase &      A &     242.2 &      66.4 & 245.0 &   9.0 &       6.6 &     1590\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Irving1972\} \\

@@

                     Laurentia &                      Central Arizona diabases -N &      A &     249.2 &      33.7 & 175.3 &  15.7 &       7.0 &   1088\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                               \textbackslash cite\{Donadini2011a\} \\

@@

                     Laurentia &                             Uinta Mountain Group &      B &     250.7 &      40.8 & 161.3 &   0.8 &       4.7 &    775\$\textasciicircum \{+25\}\$\$\_\{-25\}\$ &                                   \textbackslash cite\{Weil2006a\} \\

>>>>

             Laurentia-Wyoming &                       Sourdough mafic dike swarm &      A &    -108.3 &      44.7 & 292.0 &  49.2 &       8.1 &     1899\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Kilian2016b\} \\

@@

                     Laurentia &                                    Dubawnt Group &      B &     265.6 &      64.1 & 277.0 &   7.0 &       8.0 &   1785\$\textasciicircum \{+35\}\$\$\_\{-35\}\$ &                                   \textbackslash cite\{Park1973a\} \\

@@

                     Laurentia &                                    Cleaver Dykes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Irving2004a\} \\

@@

                     Laurentia &                          Western Channel Diabase &      A &     242.2 &      66.4 & 245.0 &   9.0 &       6.6 &     1590\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                 \textbackslash cite\{Irving1972a\} \\

@@

                     Laurentia &                      Central Arizona diabases -N &      A &     249.2 &      33.7 & 175.3 &  15.7 &       7.0 &   1088\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                               \textbackslash cite\{Donadini2011b\} \\

@@

                     Laurentia &                             Uinta Mountain Group &      B &     250.7 &      40.8 & 161.3 &   0.8 &       4.7 &    775\$\textasciicircum \{+25\}\$\$\_\{-25\}\$ &                                   \textbackslash cite\{Weil2006b\} \\
